Powering Hidden Markov Model by Generative Models

### 2019-07-21 manuscript/main.tex
add shared structure

To solve problem \autoref{opm:pi}, we formulate its Lagrange function as
\begin{equation}
  \Ll = \Qq(\bm{\Phi}; \bm{H}^{\mathrm{old}}) + \sum_{\lambda_s} \lambda_s\left( 1-  \sum_{\kappa=1}^{K}\pi_{s, \kappa}  \right).
\end{equation}
Solving $\pd{\Ll}{\pi_{s, \kappa}} = 0$ gives
\begin{equation}
  \pi_{s,\kappa} = \frac{1}{\lambda_s}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r}=s, \smtr{\kappa}{t}{r} =\kappa| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})
\end{equation}
With condition $\sum_{\kappa=1}^{K} \pi_{s, \kappa}= 1, \forall s = 1, 2, \cdots, |\Ss|$, we have
\begin{equation}
  \lambda_s = \sum_{\kappa=1}^{K}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r}=s, \smtr{\kappa}{t}{r} =\kappa | \ubmr{x}{r}; \bm{H}^{\mathrm{old}})
\end{equation}
Then the solution to \autoref{opm:pi} is
\begin{equation}\label{eq:mix-latent-parameter-solution}
  \pi_{s, \kappa} = \frac{\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r} =s, \smtr{\kappa}{t}{r}=\kappa | \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) }{\sum_{k =1}^{K}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}-1} p(\smtr{s}{t}{r} =s, \smtr{\kappa}{t}{r}=k | \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) }
\end{equation}
where $p(s, \kappa | \ubm{x}; \bm{H}^{\mathrm{old}}) = p(s| \ubm{x}; \bm{H}^{\mathrm{old}}) p(\kappa | s, \ubm{x}; \bm{H}^{\mathrm{old}})$ that can be computed by results of forward/backward and \autoref{eq:kappa-posterior}.

\textcolor{red}{I am going to put specific update formula for $\pi$ here....}

@@

@@

\subsubsection{Generator-shared HMM (GSHMM)...to be continued}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}
    \tikzstyle{enode} = [thick, draw=blue, ellipse, inner sep = 1pt,  align=center]
                                           %                                            \tikzstyle{nnode} = [thick, rectangle, rounded corners = 1pt,minimum size = 1.2cm,draw,inner sep = 2pt]
    \tikzstyle{nnode} = [thick, rectangle, rounded corners = 2pt,minimum size = 0.8cm,draw,inner sep = 2pt]
    \node[enode] (z1) at (0,1.8) {$\bm{z}\sim p_1(\bm{z})$};
    \node[enode] (z2) at (0,0.5){$\bm{z}\sim p_{2}(\bm{z})$};
    \node[enode] (zK) at (0,-1.8) {$\bm{z}\sim p_{|\Ss|}(\bm{z})$}; 
    \node[enode] (x) at (5.8,1){$\ubm{x}\sim p(\ubm{x};\bm{H})$};
                                           %                                            \node at (3,-1){$p(\bm{z}) = \sum_k\pi_kp_k(\bm{z})$};
    \node[nnode] (g) at (3.5,1) {$\bm{g}$};

\subsubsection{Generator Shared HMM (GSHMM)}

\textbf{To be continued}...

>>>>

To solve problem \autoref{opm:pi}, we formulate its Lagrange function as
\begin{equation}
  \Ll = \Qq(\bm{\Phi}; \bm{H}^{\mathrm{old}}) + \sum_{\lambda_s} \lambda_s\left( 1-  \sum_{\kappa=1}^{K}\pi_{s, \kappa}  \right).
\end{equation}
Solving $\pd{\Ll}{\pi_{s, \kappa}} = 0$ gives
\begin{equation}
  \pi_{s,\kappa} = \frac{1}{\lambda_s}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r}=s, \smtr{\kappa}{t}{r} =\kappa| \ubmr{x}{r}; \bm{H}^{\mathrm{old}})
\end{equation}
With condition $\sum_{\kappa=1}^{K} \pi_{s, \kappa}= 1, \forall s = 1, 2, \cdots, |\Ss|$, we have
\begin{equation}
  \lambda_s = \sum_{\kappa=1}^{K}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r}=s, \smtr{\kappa}{t}{r} =\kappa | \ubmr{x}{r}; \bm{H}^{\mathrm{old}})
\end{equation}
Then the solution to \autoref{opm:pi} is
\begin{equation}\label{eq:mix-latent-parameter-solution}
  \pi_{s, \kappa} = \frac{\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}} p(\smtr{s}{t}{r} =s, \smtr{\kappa}{t}{r}=\kappa | \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) }{\sum_{k =1}^{K}\sum_{r=1}^{R} \sum_{t=1}^{{T}^{(r)}-1} p(\smtr{s}{t}{r} =s, \smtr{\kappa}{t}{r}=k | \ubmr{x}{r}; \bm{H}^{\mathrm{old}}) }
\end{equation}
where $p(s, \kappa | \ubm{x}; \bm{H}^{\mathrm{old}}) = p(s| \ubm{x}; \bm{H}^{\mathrm{old}}) p(\kappa | s, \ubm{x}; \bm{H}^{\mathrm{old}})$. $p(s| \ubm{x}; \bm{H}^{\mathrm{old}})$ that can be computed by results of forward/backward and \autoref{eq:kappa-posterior}. The posterior for $\kappa$ can be obtained by
\begin{equation}
  p(\kappa | s, \ubm{x}; \bm{H}^{\mathrm{old}}) = \frac{p(\kappa, \ubm{x} | s; \bm{H}^{\mathrm{old}})}{\sum_{\kappa}{p(\kappa, \ubm{x} | s; \bm{H}^{\mathrm{old}})}} = \frac{\pi_{s, \kappa} p( \bm{x} | s; \bm{H}^{\mathrm{old}})}{\sum_{\kappa}{\pi_{s, \kappa} p(\bm{x} | s; \bm{H}^{\mathrm{old}})}}
  \end{equation}

@@

\subsubsection{Generator-tied HMM (GtHMM)}
\begin{figure}[!h]
  \centering
  \begin{tikzpicture}
    \tikzstyle{enode} = [thick, draw=blue, ellipse, inner sep = 1pt,  align=center]
                                           %                                            \tikzstyle{nnode} = [thick, rectangle, rounded corners = 1pt,minimum size = 1.2cm,draw,inner sep = 2pt]
    \tikzstyle{nnode} = [thick, rectangle, rounded corners = 2pt,minimum size = 0.8cm,draw,inner sep = 2pt]
    \node[enode] (z1) at (0,1.8) {$\bm{y}\sim p_1(\bm{y})$};
    \node[enode] (z2) at (0,0.5){$\bm{y}\sim p_{2}(\bm{y})$};
    \node[enode] (zK) at (0,-1.8) {$\bm{y}\sim p_{|\Ss|}(\bm{y})$}; 
    \node[enode] (x) at (5.8,1){$\ubm{x}\sim p(\ubm{x};\bm{H})$};
                                           %                                            \node at (3,-1){$p(\bm{z}) = \sum_k\pi_kp_k(\bm{z})$};
    \node[nnode] (g) at (3.5,1) {$\bm{g}$};

@@
